Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-04-08 man/figures/resilience_long_term.Rmd
add pvalues regression

```{r load_pkg}
library("tidyverse")
library("here")
library("scales")
library("patchwork")
library("ggrepel")
```

@@

  l <- list(#a = format(coef(m)[1], digits = 2),
            # b = format(abs(coef(m)[2]), digits = 2),
            r2 = format(summary(m)$r.squared, digits = 3));

  if (coef(m)[2] >= 0)  {
    # eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2,l)
    eq <- substitute(~~italic(r)^2~"="~r2,l)
  } else {
    # eq <- substitute(italic(y) == a - b %.% italic(x)*","~~italic(r)^2~"="~r2,l) 
    eq <- substitute(~~italic(r)^2~"="~r2,l)
  }

  as.character(as.expression(eq));                 
}

@@

summary(lm(rt_mean_mean~d_severity, data=sdf))
```

@@

```{r plot_rc}
sevRc <- plotrel(sdf, v = "rc", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rc") +
  xlab("Drought Severity") + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=-0.7, t=0, b=0, "pt"))

glance(lm(rc_mean_mean~d_severity, data=sdf))
```

@@

```{r}
df <- sdf %>% 
  dplyr::select(d_severity, rt_mean_mean, rs_mean_mean, rc_mean_mean) %>% 
  gather(key = res_metric, value,c(rt_mean_mean,rs_mean_mean,rc_mean_mean))

>>>>

```{r load_pkg}
library("tidyverse")
library("here")
library("scales")
library("patchwork")
library("ggrepel")
library("broom")
```

@@

  # l <- list(#a = format(coef(m)[1], digits = 2),
  #           # b = format(abs(coef(m)[2]), digits = 2),
  #           rvalue = format(summary(m)$r.squared, digits = 3),
  #           pvalue = format(summary(m)$coefficients[2,'Pr(>|t|)'],3));

  # eq <- substitute(~~italic(r)^2~"="~r2,l[1], "p=",l[2])

  eq2 <- substitute(~~italic(r)^2~"="~rvalue*","~italic(p)~"="~pvalue,  
                    list(rvalue = format(summary(m)$r.squared, digits = 3), 
                         pvalue = format(summary(m)$coefficients[2,4], digits = 3)))

  # if (coef(m)[2] >= 0)  {
  #   # eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2,l)
  #   eq <- substitute(~~italic(r)^2~"="~r2,l[1], "p=",l[2])
  # } else {
  #   # eq <- substitute(italic(y) == a - b %.% italic(x)*","~~italic(r)^2~"="~r2,l) 
  #   eq <- substitute(~~italic(r)^2~"="~r2,l)
  # }

  as.character(as.expression(eq2));                 
}

@@

i <- summary(lm(rt_mean_mean~d_severity, data=sdf))
```

@@

```{r plot_rc}
sevRc <- plotrel(sdf, v = "rc", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 10, coordY_eq = 0.5, titulo = "Rc") +
  xlab("Drought Severity") + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=-0.7, t=0, b=0, "pt"))
```

@@

```{r, eval=FALSE, echo=FALSE}
df <- sdf %>% 
  dplyr::select(d_severity, rt_mean_mean, rs_mean_mean, rc_mean_mean) %>% 
  gather(key = res_metric, value,c(rt_mean_mean,rs_mean_mean,rc_mean_mean))
